\titel

### 2014-03-10 presentation/presa.tex
Some initial summary/conclusions...

\begin{frame}
  \frametitle{After RFF}

  \begin{itemize}
    \item In the ``Future Work'' the authors promised to generalize to Hybrid MDPs
  \end{itemize}

@@

>>>>

@@

\begin{frame}
  \frametitle{Conclusion}

  \begin{itemize}
    \item
    \item FF-Replan introduced MDP determinization to use classical planner with uncertainty
    \item RFF used this idea to generate policies using aggregation and Monte-Carlo simulations.
    \item FF-Replan has been improved with hindsight
    \item RFF has been improved for Hybrid Probabilistic Domains
    \item Also Determinizing of POMDPs have appeared
  \end{itemize}
